---
output: rmarkdown::github_document
---

# tlsh

Local Sensitivity Hashing Using the 'Trend Micro' 'TLSH' Implementation

## Description

'Trend Micro' provides an open source library <https://github.com/trendmicro/tlsh/> for local sensitivity hashing. Methods are provided to compute and compare hashes from character/byte streams.
   
## References

- Jonathan Oliver, Chun Cheng and Yanggui Chen,
   "[TLSH - A Locality Sensitive Hash](https://github.com/trendmicro/tlsh/blob/master/TLSH_CTC_final.pdf)"
   4th Cybercrime and Trustworthy Computing Workshop, Sydney, November 2013
- Jonathan Oliver, Scott Forman and Chun Cheng,
  "[Using Randomization to Attack Similarity Digests](https://github.com/trendmicro/tlsh/blob/master/Attacking_LSH_and_Sim_Dig.pdf)"
  Applications and Techniques in Information Security. Springer Berlin Heidelberg, 2014. 199-210.
- Jonathan Oliver and Jayson Pryde's
   [Trend Micro Blog Post](http://blog.trendmicro.com/trendlabs-security-intelligence/smart-whitelisting-using-locality-sensitive-hashing/)

## TODO

- [ ] File input
- [ ] Docs
- [ ] Tests
- [ ] Reference class-backed DSL

## What's Inside The Tin

The following functions are implemented:

- `tlsh_simple_diff`:	Compute TLSH hash for a character or raw vector and return hash fingerprint
- `tlsh_simple_hash`:	Compute TLSH hash for a character or raw vector and return hash fingerprint

TODO: Document DSL

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/tlsh")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(tlsh)

# current verison
packageVersion("tlsh")

```

## Example

- `index.html` is a static copy of a blog main page with a bunch of `<div>`s with article snippets
- `index1.html` is the same file as `index.htmnl` with a changed cache timestamp at the end
- `index2.html` is the same file as `index.html` with one article snippet removed
- `RMacOSX-FAQ.html` is the CRAN 'R for Mac OS X FAQ'

```{r}
doc1 <- as.character(xml2::read_html(system.file("extdat", "index.html", package="tlsh")))
doc2 <- as.character(xml2::read_html(system.file("extdat", "index1.html", package="tlsh")))
doc3 <- as.character(xml2::read_html(system.file("extdat", "index2.html", package="tlsh")))
doc4 <- as.character(xml2::read_html(system.file("extdat", "RMacOSX-FAQ.html", package="tlsh")))

# generate hashes
 
(h1 <- tlsh_simple_hash(doc1))

(h2 <- tlsh_simple_hash(doc2))

(h3 <- tlsh_simple_hash(doc3))

(h4 <- tlsh_simple_hash(doc4))

# compute distance

tlsh_simple_diff(h1, h2)

tlsh_simple_diff(h1, h3)

tlsh_simple_diff(h1, h4)
```

### Reference class machinations

Just a demo for testing purposes. This will be abstraced by a DSL.

```{r}
x <- new(Tlsh$tlsh_r)

x$lib_version()

doc1 <- charToRaw(as.character(xml2::read_html(system.file("extdat", "index.html", package="tlsh"))))

x$all_in_one(doc1)

x$update(doc1)
x$final(0)
x$is_valid()

x$get_hash()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.